location-ratings

### 2016-08-03 eda/business-attributes.Rmd
updates in attributes

```{r}
us_business <- read_csv('../clean_data/us-business.csv')
noise_level <- read_csv('../clean_data/noise-attr.csv')
attire_type <- read_csv('../clean_data/attire-attr.csv')
states <- map_data('state')
ggplot(states) + 
  geom_polygon(aes(x = long, 
                   y = lat, 
                   group = group), 
               fill = "grey80", 
               color = "white") + 
  coord_fixed(1.3) + 
  geom_point(data = us_business, 
             aes(long, 
                 lat, 
                 color = factor(stars), 
                 size = count), 
             alpha = 0.7) + 
  guides(colour = guide_legend("Star Rating"), 
         size = guide_legend("Review Counts")) + 
  labs(title = "Restaurant Reviews in United States") +
  theme_nothing(legend = TRUE)
```

>>>>

```{r}
us_business <- read_csv('us-business.csv')
noise_level <- read_csv('noise-attr.csv') 
attire_type <- read_csv('attire-attr.csv')
states <- map_data('state')
ggplot(states) + 
  geom_polygon(aes(x = long, 
                   y = lat, 
                   group = group), 
               fill = "grey80", 
               color = "white") + 
  coord_fixed(1.3) + 
  geom_point(data = us_business, 
             aes(long, 
                 lat, 
                 color = factor(stars), 
                 size = count), 
             alpha = 0.7) + 
  guides(colour = guide_legend("Star Rating"), 
         size = guide_legend("Review Counts")) + 
  labs(title = "Restaurant Reviews in United States") +
  theme_nothing(legend = TRUE)
```

### 2016-08-03 eda/location-ratings.Rmd
updates in attributes

```{r}
user_reviews <- read_csv("user-reviews.csv")
ggplot(user_reviews, aes(x = max_review,
                         y = val)) +
  geom_bar(stat = "identity", 
           position = "dodge") + 
  facet_wrap(~name) + 
  labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
  xlab("Location") + 
  ylab("Star Ratings") +
  scale_x_discrete(labels=c("Travelling", "Home"))
  scale_x_discrete(labels=c("Travelling", "Home"))
```

>>>>

```{r}
user_reviews <- read_csv("../clean_data/user-reviews.csv")
ggplot(user_reviews, aes(x = max_review,
                         y = val)) +
  geom_bar(stat = "identity", 
           position = "dodge") + 
  facet_wrap(~name) + 
  labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
  xlab("Location") + 
  ylab("Star Ratings") +
  scale_x_discrete(labels=c("Travelling", "Home"))
  scale_x_discrete(labels=c("Travelling", "Home"))
```
